Detecting changes in dispersion in COVID-19 incidence time series using a negative binomial model

### 2023-05-18 noise_covid_v2.Rmd
Edit scripts sourced in Rmd file

In this case, we use a log link function:
$$log(E[Y_i]/n_i) = \beta_1h_1(t_i) + \beta_2h_2(t_i) + \beta_3h_3(t_i)$$
  $$log(E[Y_i])-log(n_i) = \beta_1h_1(t_i) + \beta_2h_2(t_i) + \beta_3h_3(t_i)$$
  $$log(E[Y_i]) = \beta_1(h_1(t_i) + \beta_2h_2(t_i) + \beta_3h_3(t_i) + log(n_i)$$
## IRLS

@@

```{r}
par(mfrow = c(1,2))
state <- "NY"
source("code/squared.res_v_squared.fitted.R")

state <- "FL"
source("code/squared.res_v_squared.fitted.R")
```

@@

state <- "FL"
source("code/lrt_counties.R")
FL_sig <- print(which(pvals < 0.05))

```

>>>>

In this case, we use a log link function:
$$log(E[Y_i]/n_i) = \beta_1h_1(t_i) + \beta_2h_2(t_i) + \beta_3h_3(t_i)$$
  $$log(E[Y_i])-log(n_i) = \beta_1h_1(t_i) + \beta_2h_2(t_i) + \beta_3h_3(t_i)$$
  $$log(E[Y_i]) = \beta_1(h_1(t_i) + \beta_2h_2(t_i) + \beta_3h_3(t_i) + log(n_i)$$

## IRLS

@@

@@

state <- "FL"
source("code/lrt_counties.R")
FL_sig <- (which(pvals < 0.05))
```

```{r}
signif_index <- c(NY_sig, FL_sig)

state <- "NY"
source("code/squared.res_v_squared.fitted.R")

state <- "FL"
source("code/squared.res_v_squared.fitted.R")

source("code/vis_signific_state.R")
```
```{r}
# disp_stats <- c()
# for (i in 1:dim(new_cases_subset[state_index])[1]){
#   Y <- new_cases_subset[i,]
#   spline_mod.1.pois <- spl_fit_pois(Y = Y, population=ny_fl_df_t$populations[i], inds=1:(length(Y)/2))
#   disp_stats <- c(disp_stats, spline_mod.1.pois$deviance/spline_mod.1.pois$df.residual)
# }
```

```{r}
# library(tigris)
# p <- round(fl_df_t$p, digits=1)
# p[is.na(p)] <- "na"
# fl$p <- p 
# 
# ggplot(fl) +
#   geom_sf(aes(fill=p))
```
